Impact of Assessment Format on Student Learning Outcomes

### 2019-04-16 CUT/paper.tex
Document formatting

\usepackage{hyperref}
\usepackage{apacite}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\doublespace
\title{Working Title - CUT Research Paper}
\author{W. Justin Toth}
\begin{document}
\maketitle
\begin{abstract}
We study of question of how assessment formats impact student study behaviours, learning outcomes, and perception of the courses they take. We particularly focus on Mathematics and Science courses, but the findings in this survey are general enough to be widely applicable. We study Multiple Choice versus Constructed Response, how much Reference Material to allow in the exam room, Oral versus Written Exams, and the Two Stage method for injecting collaborative learning into exams.
\end{abstract}
\tableofcontents
\section{Introduction}

@@

In~\cite{videnovic2017oral} the author interviews $7$ mathematics professors of different culture backgrounds about the their perspectives on Written versus Oral Exams. One common point of agreement found among the subjects were type of skills each exam format was better suited for. Mathematical skills can broadly be categorized into one of two types: Procedural or Conceptual. Procedural skills reflect technical competency with the instruments of Mathematics. An example of a question testing Procedural knowledge would be ``Compute the integral $\int\sec x dx.$". Conceptual skills reflect understanding of the ways in which individual units of mathematical fact interrelate and support each other. For example, ``What does a matrix being invertible tell you about its determinant, and consequently its eigenvalues?". In Videnovic's survey, it was widely agreed that Written Exams are more proficient in testing Procedural skills, and Oral Exams more proficient in testing Conceptual skills.

@@

\bibliographystyle{apacite}
\bibliography{references.bib}

>>>>

\usepackage{hyperref}
\usepackage{apacite}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\doublespace
\title{Impact of Assessment Format on Student Learning Outcomes}
\author{W. Justin Toth\\Combinatorics and Optimization\\20411831}
\begin{document}
\maketitle
\begin{abstract}
We study of question of how assessment formats impact student study behaviours, learning outcomes, and perception of the courses they take. We particularly focus on Mathematics and Science courses, but the findings in this survey are general enough to be widely applicable. We study Multiple Choice versus Constructed Response, how much Reference Material to allow in the exam room, Oral versus Written Exams, and the Two Stage method for injecting collaborative learning into exams.
\end{abstract}
\newpage
\tableofcontents
\newpage
\section{Introduction}

@@

In~\cite{videnovic2017oral} the author interviews seven mathematics professors of different culture backgrounds about the their perspectives on Written versus Oral Exams. One common point of agreement found among the subjects were type of skills each exam format was better suited for. Mathematical skills can broadly be categorized into one of two types: Procedural or Conceptual. Procedural skills reflect technical competency with the instruments of Mathematics. An example of a question testing Procedural knowledge would be ``Compute the integral $\int\sec x dx.$". Conceptual skills reflect understanding of the ways in which individual units of mathematical fact interrelate and support each other. For example, ``What does a matrix being invertible tell you about its determinant, and consequently its eigenvalues?". In Videnovic's survey, it was widely agreed that Written Exams are more proficient in testing Procedural skills, and Oral Exams more proficient in testing Conceptual skills.

@@

\newpage
\bibliographystyle{apacite}
\bibliography{references.bib}
